Box

### 2021-07-11 MS/box.Rmd
inconsistency fixed

$$
\text{ARR} = \frac{\overline{X}_{1} - \overline{X}_{2}}{T_2 - T_1},
$$

where *T* stands for temperature in Celsius and $T_2 > T_1$, and $\overline{X}_1$ and $\overline{X}_2$ are the average physiological responses at two temperature points $T_1$ and $T_2$.

<!--- Dan we may need to use bar_X rather than just X or M for consistence in the main text --->

To obtain the sampling variance for this equation (slope), we will need to know several basic properties of variance. Let's assume $X_1$ is a random variable which means that this variable has a mean and standard deviation (variance). Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X$. This can be summarized as:

@@

Therefore, when $X_1$ and $X_2$ are indepedent, we can obtain the sampling variance for ARR as:

@@

Finally, we note that by using the basic properties of variance and the delta method, one can derive sampling variance for most of cases. Indeed, these were enough for us to derive samping variance for 'new' effect sizes (e.g. $lnQ_{10}$; see the main text) and as in Nakagawa et al. (2015, MEE) and Senior et al. (2020, RSM).

>>>>

$$
\text{ARR} = \frac{X_{1} - X_{2}}{T_2 - T_1},
$$

where *T* stands for temperature in Celsius and $T_2 > T_1$, and $X_1$ and $X_2$ are the average physiological responses (estimated means) at two temperature points $T_1$ and $T_2$.

To obtain the sampling variance for this equation (slope), we will need to know several basic properties of variance. Let's assume $X_1$ is a random variable, which means that this variable has a mean and standard deviation (variance). Multiplying a constant ($a$) will change the variance by the square of that constant ($a^2$) while adding or subtracting the constant ($b$) does not change the variance of $X$. This can be summarized as:

@@

Therefore, when $X_1$ and $X_2$ are independent, we can obtain the sampling variance for ARR as:

@@

Finally, we note that by using the basic properties of variance and the delta method, one can derive sampling variance for most of cases. Indeed, these were enough for us to derive sampling variance for 'new' effect sizes (e.g. $lnQ_{10}$; see the main text) and as in Nakagawa et al. (2015, MEE) and Senior et al. (2020, RSM).
